Mann-Whitney-Wilcoxon test with `hyper3` objects

### 2022-08-07 inst/mann_whitney_wilcoxon.Rmd
more work

Now some permutation tests under the null:

```{r,repeat_mww_H0,cache=TRUE}
n <- 100
mww_pval <- rep(NA,n)
for(i in seq_len(n)){
      jj <- sample(c(x,y))
      xstar <- jj[seq(from=1,length=length(x))]
      ystar <- jj[seq(from=length(x)+1,to=length(x)+length(y))]
      mww_pval[i] <- suppressWarnings(wilcox.test(xstar,ystar)$p.value)
}
```

```{r,histmww}
mww_pval
hist(mww_pval)
```

```{r,repeat_hyper3_H0,cache=TRUE}
n <- 100
hyper3_pval <- rep(NA,n)
for(i in seq_len(n)){
      jj <- sample(c(x,y))
      xstar <- jj[seq(from=1,length=length(x))]
      ystar <- jj[seq(from=length(x)+1,to=length(x)+length(y))]
      hyper3_pval[i] <- equalp.test(ordervec2supp3(args2ordervec(x=xstar,y=ystar)))$p.value
}
```

```{r,histhyper3}
hist(hyper3_pval)
ks.test(hyper3_pval,"punif")

plot(ecdf(hyper3_pval))
par(pty="s")
qqplot(mww_pval,hyper3_pval,asp=1)
abline(0,1)
```

@@

```{r,showpvals}
a
plot(a)
table(a[,1]<0.05,a[,2]<0.05)
```

>>>>

#  Some permutation tests under the null:

```{r,dosomepvalsNULL,cache=TRUE}
n <- 100
a <- matrix(0,n,2)
colnames(a) <- c("mww","hyper3")
for(i in seq_len(n)){
  d <- rrace3(pn=c(a=10,b=10),ps=c(a=0.5,b=0.5))  #null 
  jj <- seq_along(d)
  a[i,1] <- wilcox.test(jj[d=="a"],jj[d=="b"])$p.value
  a[i,2] <- equalp.test(ordervec2supp3(d))$p.value
}
```

```{r,showpvalsNULL}
head(a)
par(pty="s")
plot(log10(a),asp=1,xlim=c(-2,0),ylim=c(-2,0),main="p-values under the NULL (log scale)",
xlab="log(p),Wilcox",ylab="log(p), hyper3")
abline(0,1)
plot(a,asp=1,xlim=c(0,1),ylim=c(0,1),main="p-values under the NULL (linear scale)",xlab="p,Wilcox",ylab="p,hyper3")
abline(0,1)
(size_wilcox <- sum(a[,1]<0.05)/nrow(a))
(size_hyper3 <- sum(a[,2]<0.05)/nrow(a))

table(type_I_wilcox=a[,1]<0.05,type_I_hyper3=a[,2]<0.05)
```

# Some permutation tests under the alternative

@@

```{r,showpvals}
head(a)
par(pty="s")
plot(log10(a),asp=1,xlim=c(-4,0),ylim=c(-4,0))
abline(0,1)
(power_wilcox <- sum(a[,1]<0.05)/nrow(a))
(power_hyper3 <- sum(a[,2]<0.05)/nrow(a))

table(wilcox=a[,1]<0.05,hyper3=a[,2]<0.05)
```
